%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Treasurer, Board of Directors} % Job title
    {Noisebridge Hackerspace} % Organization
    {San Francisco, CA} % Location
    {November 2017 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Develop and maintain financial policies, records, and systems to provide data analysis for the benefit of achieving the organization's long term objectives.}
        \item {Evaluate and revitalize performance of operational procedures, annual reviews, and financial reporting.}
        \item {Elected to Treasurer June 2018; Re-elected to Board July 2018}       
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Fundraising Project Manager} % Job title
    {Noisebridge Hackerspace} % Organization
    {San Francisco, CA} % Location
    {2016 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Forged partnership with Seattle-based fundraising firm to develop growth strategies to raise funds for purchasing a building in San Francisco.}
        \item {Launched grassroots fundraising campaign using Agile development which increased funding runway from 3 months to 18+ months.}
        \item {Mobilized active community engagement in grant research and proposal writing.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Instructional Assistant} % Job title
    {General Assembly} % Organization
    {San Francisco, CA} % Location
    {February 2015 - November 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Provided one-on-one mentorship, office hours, identified gaps in skill sets and worked with students to create achievable minimum viable products for each project.}
        \item {Mentored students and enabled resourcefulness in learning JavaScript, Node.js, Ruby on Rails, OOP, databases, APIs, and DOM manipulation in Back End Web Development, Front End Web Development, and JavaScript Development using ES6.}
        \item {Managed version controlled repositories for 9 cohorts of up to 33 students to commit assignments via pull request for code review.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Web Development Educator, Event Organizer} % Job title
    {freeCodeCamp} % Organization
    {San Francisco} % Location
    {February 2015 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Award-winner for top 100 contributors of resources, curriculum, and community.}
        \item {Established the San Francisco chapter with weekly events for anyone learning to code.}
        \item {Enabled four other California chapters to develop using San Francisco chapter's resources: Sacramento, Oakland, Redwood City, and Santa Clara.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Full Stack Web Developer, Data Analyst} % Job title
    {Oregon Research Institute} % Organization
    {San Francisco, CA, Remote} % Location
    {March 2015 - May 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Contributed to a custom RESTful web framework and API to provide interactive internet study interventions for hard to reach populations for social science research.}
        \item {Mapped testing suites to support legacy projects using best practices, OOP, and Agile development.}
      \end{cvitems}
      %\begin{cvsubentries}
      %  \cvsubentry{}{KNOX(Solution for Enterprise Mobile Security) Penetration Testing}{Sep. 2013}{}
      %  \cvsubentry{}{Smart TV Penetration Testing}{Mar. 2011 - Oct. 2011}{}
      %\end{cvsubentries}
    }

%---------------------------------------------------------
\end{cventries}
